{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-03 Paper/main.tex
small corrections

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^k \quad i \in \mathcal{I}
	\end{equation}
	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation. The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. Therefore, regarding the use, this may be useful for relatively simple functions. However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities. Moreover, it leads to an undesirable behavior at the tails such as Taylor expansion. (cf. \cite{ramsay_functional_2005})

@@

	Therefore, its basis functions inherits a repeating behavior which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.  {\color{blue} Motivate from Fourier series}

>>>>

	Each curve $x_i(t)$ exists $\forall t \in [T_1, T_2]$, but is only observed at discrete measurement points. As it can be seen, the measurmant points can be differentiated through each sample. However, this is not a primary interest of this paper, and, therefore, we consider the case where every measurement point exists evenly, namely, that $t_{i,j}$ and $J_i$ are identical for all $i$. In principal, the recorded functional data can be seen as a set of discretized realizations of a random function since it is finitely countable. It causes necessities to represent the functional data with respect to some expansion technique. The several techniques to make the functional data smooth is introduced on the following sub-chapters.\\
	As in the finite dimensional setting, the concept of identically distributed and independent data is important for the functional data analysis. The random functions share the identical and independent distribution, which makes the statistical inferential procedures possible. An example of such a data set could be the data set of 60 NIR-spectra of gasoline samples in which each spectra was randomly selected and evenly measured.

@@

	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
	\end{equation}
	where the shift parameter $\alpha$ is specified to be the center of the interval subject to approximation. The first order function within the monomial basis system, for $k=0$, is called the constant basis system (cf. \cite{horvath_inference_2012}). There exist collinearity problems of this basis system since the monomial basis functions become more correlated to each other as the degrees increase, which would result in numerically unstable situation. This restricts the number of basis functions. However, the lower order monomial function makes it impracticable to capture pronounced local peculiarities. It finally leads to an undesirable behavior at the tails such as Taylor expansion (cf. \cite{ramsay_functional_2005}). Therefore, regarding the use, this may be useful for relatively simple functions.

@@

	Therefore, its basis functions inherits a repeating behavior which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthonormal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.
